Staged Abstract Interpreters

### 2018-11-04 paper/20_bg.tex
typo
cache type class

In this section, we first described the language we will model and analyze, and present a unstaged concrete 
interpreter for it. Then, starting from this unstaged concrete interpreter, we proceed in two directions:
by abstracting it we obtain an unstaged abstract interpreter; by staging it we obtain a staged concrete
interpreter.

@@

The evaluator \texttt{eval} is a open-recursive function that takes one and three arguments: the first
one \texttt{ev} represents the recursive function itself; the rest three are the AST representing program 
will be executed, the environment that maps from identifiers to addresses, and the store that maps addresses to values.
The interpreters that take control, environment and store components also can be obtained by 
refunctionalizing \cite{DBLP:conf/ppdp/AgerBDM03, Wei:2018:RAA:3243631.3236800} a small-step CESK 
machine \cite{DBLP:conf/popl/FelleisenF87}.
We provide a function \texttt{fix} to close the recursion by providing the result of \texttt{fix(ev)} 
to argument \texttt{ev}. Finally, a default implementation for the top-level evaluation function \texttt{eval\_top} is defined.
As we will see later, the open-recursion style is beneficial when implementing abstract interpreter and 
staged abstract interpreter \todo{cite adi}.

>>>>

In this section, we first described the language we will model and analyze, and present an unstaged concrete 
interpreter for it. Then, starting from this unstaged concrete interpreter, we proceed in two directions:
by abstracting it we obtain an unstaged abstract interpreter; by staging it we obtain a staged concrete
interpreter.

@@

The evaluator \texttt{eval} is a open-recursive function that takes one and three arguments: the first
one \texttt{ev} represents the recursive function itself; the rest three are the AST representing program 
will be executed, the environment that maps from identifiers to addresses, and the store that maps addresses to values.
This environment-and-store-passing style big-interpreter also can be obtained by 
refunctionalizing \cite{DBLP:conf/ppdp/AgerBDM03, Wei:2018:RAA:3243631.3236800} a small-step CESK 
machine \cite{DBLP:conf/popl/FelleisenF87}.
We provide a function \texttt{fix} to close the recursion by providing the result of \texttt{fix(ev)} 
to argument \texttt{ev}. Finally, a default implementation for the top-level evaluation function \texttt{eval\_top} is defined.
As we will see later, the open-recursion style is beneficial when implementing abstract interpreter and 
staged abstract interpreter \todo{cite adi}.
